\mytitile\\~

### 2020-01-21 document.tex
Yursa's edits

	\author{O.V. Astafiev}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia 
	}
	\affiliation{Skolkovo Institute of Science 
	and Technology, Moscow, Russian Federation}
	\affiliation{Physics Department, Royal 
	Holloway, University of London, Egham, Surrey 
	TW20 0EX, United Kingdom}
%

@@

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws\cite{you2011atomic}. Due to synthetic nature 
of SAAs, their Hamiltonians can be pre-designed 
and engineered which makes them a particularly 
versatile tool for studies in quantum optics. 
Notably, high controllability of their parameters 
allows direct observation of novel physical 
effects previously inaccessible for natural 
systems.

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs\cite{hutchings2017tunable} ($E^1_{J, 
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
$E^{1,2}_C/h = 220$ MHz, $d^{1,2} =0.75$) coupled 
to a single notch-type\cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples\cite{majer2007coupling} the transmons and 
allows joint\cite{chow2010detecting} readout of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown 
depicting the layout of the components. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw''\cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in colour on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

\begin{figure}
	 	\includegraphics[width=\linewidth]{experiment_2}
	\caption{\textbf{(a)} Optical photograph of 
	the device (false coloured). Two transmons 
	(orange, 1 and blue, 2) are coupled 
	capacitively to a $\lambda/4$ coplanar 
	resonator. Frequency control lines come from 
	both sides, and from below a waveguide for 
	microwave excitation  is connected (green). 
	\textbf{(b)} The equivalent electrical 
	circuit. Tunable Josephson junctions are 
	SQUIDs with magnetic flux control. 
	\textbf{(c)} Frequencies of the fundamental 
	transitions of the transmons $\omega_1(I)$ 
	and $\omega_2(I)$ depending on the current 
	$I$ in an external coil when correctly 
	aligned by the individual flux control lines. 
	In this work, we focus on the area inside the 
	dashed rectangle.}
	\label{fig:experiment}
\end{figure}

@@

The readout resonator is not included in the 
model since in the dispersive regime it does not 
affect the dynamics of the SAM. Hence, the 
readout is modelled just by some measurement 
operator $\hat M(f_p)$ that can be obtained by 
finding the transmission $S_{21}(f_p)$ ($f_p$ is 
the probe frequency near the resonance) through 
the sample after preparing various states of the 
SAM. Another way to find $\hat M(f_p)$ is to 
calculate $S_{21}(f_p)$ via offsetting the 
experimental resonance curve measured when the 
SAM is in the ground state by the dispersive 
shifts corresponding to the SAM basis 
states\cite{filipp2009two}. Since we have not 
directly measured these dispersive shifts, in our 
modelling they are treated as fitting parameters. 
Finally, the observable value for any state $\hat 
\rho$ is calculated as $S_{21}^{sim}(f_p) = 
\Tr[\hat M(f_p) \hat \rho]$.

@@

	\includegraphics[width=.7\linewidth]{powerscan_1d}
	\caption{Power dependence of feature II: 
	experiment, simulation and analytic model. Dashed are the model curves turning to dotted when the 
	model is not expected to be valid (see 
	Sections \ref{sec:theory} and 
	\ref{sec:münchhausen}); model values for 
	$\Omega_{1,2}$ are the same for both (a) and 
	(b): $\Omega_{1,2}/2\pi=$ 4.5, 11.25, 22.5 
	and 45 MHz. \textbf{(a)} Experiment (second 
	cooldown; the parameters are different to 
	those in \autoref{fig:experiment}). The power 
	of the microwave source is increased from -20 
	to 0 dBm, and the corresponding growth of the 
	splitting and the widths of the spectral 
	lines is observed. \textbf{(b)} Simulation 
	with amplitudes of the driving $\Omega_{1,2}$ 
	equal to the model values; other parameters 
	as in \autoref{fig:two-tone}. Note that now 
	colours show the population of the ground 
	state. \textbf{(c)} Linear dependence of the 
	splitting size on the driving voltage of the 
	microwave source $V_{rms} = 
	\sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 
	50\ \Omega}$, ${\Omega_2}/{V_{rms}} = 0.23\ 
	{\text{MHz}}/{\text{mV}}$. From Section 
	\ref{sec:theory}, the splitting size is 
	$\frac{2\sqrt{3}}{3} \Omega_2$.}
	\label{fig:zoom}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{topological_splittings}
	\caption{Simulated population of the ground 
	state when the transmons are driven at the 
	same frequency but at different amplitudes 
	$\Omega_{1,2}$. In the top row (middle row), 
	$\Omega_{1(2)}$ is increased while 
	$\Omega_{2(1)} = \text{const} \ll 
	\Omega_{1(2)}$; two topologically different 
	types of anticrossings arise depending on 
	which transmon is driven stronger. In the 
	bottom row, we show how the splittings vanish 
	when the weaker driving is increased to match 
	with the stronger one. Gray dashed lines show 
	the solution without driving, in black are 
	the model curves based on Sections 
	\ref{sec:theory} and \ref{sec:münchhausen}.}
	\label{fig:difdrive}
\end{figure*}

@@

\paragraph{Identification of the spectral lines.} 
Though it is not possible to describe all of the 
experimental features with the unperturbed model, 
we can still use it to identify most of the 
observed transitions as follows. As said above, 
by numerical diagonalization, we calculate the 
unperturbed frequencies of the undriven SAM as 
$\omega_{mn} = (E_n - E_m)/h$ where $n>m,\  
n,m=0..9$. In \autoref{fig:two-tone}~(d), we 
place them over the heatmap data depicting the 
population of $\ket{10}$ optionally dividing 
$\omega_{mn}$ by some integer $n$ to find the 
frequency of an $n$-photon process to find a 
match among the visible lines in the heatmap. 
Since the number of SAM states is finite, we can 
quickly find all such correspondences.

@@

Having settled the naming system, we continue to 
analyse the plots. Due to the strong driving, we 
observe several multiphoton transitions besides 
the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
$01$ and $10$ lines). The ${02/2}$ and ${20/2}$ 
are very commonly found for transmons and lie 
$|\alpha_{(1,2)}|/2$ lower than the main lines 
$\omega_{(1,2)}(I)$. Another two-photon process 
appears as $11/2$ line when two SAAs are excited 
simultaneously. This process is used, for 
example, for doing the bSWAP 
gate\cite{poletto2012entanglement}; in our case, 
it is taking part in formation of feature I. A 
three-photon process $12/3$ is also clearly 
visible just below the $02/2$ line. As we will 
see, it is involved in forming features II and 
III. Notably, transitions $11/2$, ${21/3}$ and 
${12/3}$ are forbidden when there is no 
interaction between transmons ($J=0$). Therefore, 
it is expected that all Roman-numbered features 
should only appear with non-vanishing $\hat 
H_{int}$.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} 
	Schematic of the transition frequencies near 
	III (not to scale). Red dashed line shows the 
	current (0.36 mA) where the first transmon 
	(orange) is below the second one (blue) 
	exactly by $\alpha_2/2$ and several 
	transitions become resonant. Here we assume 
	that each transmon is driven at its own 
	frequency. \textbf{(b)} System level 
	structure at the resonant point and the first transmon 
	driving of amplitude $\Omega_1$ 
	(orange ellipses) at a small detuning 
	$\Delta_1$ from $\omega_1$. The second 
	transmon driving is not shown here. Action of 
	$\hat H_{int}$ in RWA is depicted as 
	orange-blue circles. \textbf{(c)} In the 
	frame rotating with $\hat 
	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
	become nearly degenerate ($\omega_1 
	\rightarrow \Delta_1$). Dressing increases this splitting to 
	$\Omega_1^R = \sqrt{\Omega_1^2 + 
	\Delta_1^2}$. \textbf{(d)} Transitions in the 
	dressed system induced by $\hat 
	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
	the left part of the panel, all possible 
	two-photon transitions near $\omega_1$ are 
	depicted: the blue transitions are not 
	shifted in frequency, the light blue ones are shifted 
	by $\pm\Omega^R_1/2$. In the right 
	part, the most contributing trajectories are 
	depicted; gray crosses show transitions that 
	are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on which transitions
are involved in the A-T-like effect for feature III. 
For simplicity, we will temporarily assume that 
each transmon is driven at its own frequency 
(this assumption will be lifted in the following 
section). For convenience, in 
\autoref{fig:main_scheme}~(a) we schematically 
reproduce the transitions near III where the 
first transmon (orange) is below the second 
(blue), and the resonance point in current is 
shown with a dashed red line. Next, 
\autoref{fig:main_scheme}~(b) demonstrates the 
level structure of the SAM at 0.36 mA. Detuned by 
$\Delta_1$ from $10$, single-photon driving of 
$\hat H_d^1$ is shown with orange ellipses while 
much weaker two-photon $\hat H_d^2$ is not shown 
yet. Since from numerical simulations we know 
that the third level of the first transmon is not 
necessary to observe the splitting, $\ket{20}$ is 
shown transparent, and states $\ket{21},\ 
\ket{22}$ are not shown.

@@

As one can see from \autoref{fig:difdrive}, only the two-photon transition $11/2$ is affected and deviates from unperturbed spectrum when approaching the 01-10 intersection while the other spectral lines are not moving. Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b). We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously; this is clearly visible in \autoref{fig:difdrive}. Instead, we observe one line to the left and the other to the right from the 01-10 intersection.

@@

The upper branch of the fitted anticrossing is expected to deviate from the model (see dashed curves in \autoref{fig:zoom}) because of the avoided crossing marked as the secondary feature 3 which was not incorporated in the simple linear model. The small discrepancy between the experimental and simulated data in the upper branch is caused by a slight elevation of the lower sweet spot of the first transmon moving the avoided crossing 3 closer to the feature II; however, it is not important for our reasoning.

@@

Another interesting effect occurs when both 
components of the driving operator are in the 
single-photon regime. Now, both transmons are 
dressed and probed simultaneously. In this case, 
the $11/2$ transition is split at the resonance 
into a hyperbolic curve, never forming a doublet 
in frequency. Moreover, its shape and visibility 
depends qualitatively on the relation between the driving 
amplitudes; for instant, if they are equal, it disappears 
completely. In our sample, we have a fixed ratio 
of approximately 2 between $\Omega_1$ and 
$\Omega_2$ which still allows us to distinguish the 
splitting experimentally. Notably, the frequency of $11/2$ transition far 
from resonance is also changed noticeably with 
changing power, which means that a fast bSWAP 
gate should be performed at a different frequency 
than the unperturbed model predicts.

@@

\begin{figure}[b]	
	\includegraphics[width=\linewidth]{intro_scheme}
	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame ($\hbar=1$ here). \textbf{(a)} A three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$ which induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$. \textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$. However, when the RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$. Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ at frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.} 
	\label{fig:at-standard}
\end{figure}

\paragraph{Classical derivation.} In the classical case, the mathematical description goes as follows. At first, there is a three-level system which is driven by a strong radiation with an amplitude $\Omega_1$ at a frequency detuned by $\Delta$ from the $\ket{0}\rightarrow \ket{1}$ transition with a frequency $\omega_{01}$ (the \textit{coupler} tone). Additionally, we have a weak probe radiation at a frequency $\omega_{p}$ and with an amplitude $\Omega_2$ between $\ket{1}$ and $\ket{2}$ (the \textit{probe} tone). This step is illustrated in \autoref{fig:at-standard}~(a). The Hamiltonian for such system is as follows:

\begin{equation*}
\hat H^c_0/\hbar = \left[\begin{matrix}
0 & \Omega_{1} \cos{\left(\omega_{01}- \Delta \right)t} & 0\\
\Omega_{1} \cos{\left(\omega_{01} - \Delta \right)t}   & \omega_{01} &\Omega_{2} \cos\omega_p t  \\
0 & \Omega_{2} \cos{\omega_p t}  & \omega_{02}\end{matrix}\right].
\end{equation*}

Next, we move to the rotating frame by using an operator
\[
\hat R = \left[\begin{matrix} 
1 & 0 & 0\\0 & e^{- i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{- i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
\]
Note here that level $\ket{2}$ is also rotated: this is convenient to preserve the frequency of the driving term with $\Omega_2$. The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat R^\dag \hat H_0 \hat R - i \hat{R}^\dag \partial_t  \hat R$. The level structure without driving  is shown in the left part of \autoref{fig:at-standard}~(b). Applying the RWA, we obtain:
\begin{equation*}
\hat H^c_1/\hbar = \left[\begin{matrix}0 &\Omega_{1}/2 & 0\\\Omega_{1}/2 & \Delta & \Omega_{2} e^{i t \omega_p}/2\\0 & \Omega_{2} e^{-i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
\end{equation*}

@@

\begin{equation*}
\hat H^c_3/\hbar = \left[\begin{matrix} 
\frac{\Delta}{2} - \frac{\sqrt{\Delta^{2} + \Omega_{1}^{2}}}{2} & 
0 &
\frac{\Omega_{2} e^{i t \omega_{p}}}{2}\sin(\theta)
\\
0 & 
\frac{\Delta}{2} + \frac{\sqrt{\Delta^{2} + \Omega_{1}^{2}}}{2} & 
\frac{\Omega_{2} e^ {i t \omega_p}}{2}\cos(\theta)
\\
\frac{\Omega_{2} e^{-i t \omega_{p}} }{2}\sin(\theta) & 
\frac{\Omega_{2} e^{-i t \omega_{p}}}{2} \cos(\theta) & 
\omega_{12} +\Delta 
\end{matrix}\right].
\end{equation*}

One may see that now resonant conditions for the probe drive are $\omega_p = \omega_{12} + \dfrac{(\Delta \pm \Omega^R)}{2}$, where $\Omega^R = \sqrt{\Omega_1^2 + \Delta^2}$, $\omega_{12} = \omega_{02}- \omega_{01}$, and its amplitude is renormalized by an angle $\theta,\ \tan 2\theta = -\frac{\Omega_1}{\Delta}$.

>>>>

	\author{O.V. Astafiev}
	\affiliation{Skolkovo Institute of Science 
		and Technology, Moscow, Russian Federation}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia}
	\affiliation{Physics Department, Royal 
	Holloway, University of London, Egham, Surrey 
	TW20 0EX, United Kingdom}
\affiliation{National Physical Laboratory, Teddington, TW11 0LW, United Kingdom}
%

@@

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws\cite{you2011atomic}. Their Hamiltonians can be pre-designed 
and engineered which makes them a particularly 
versatile tool for studies in quantum optics, and high controllability of their parameters 
allows direct observation of novel physical 
effects previously inaccessible for natural 
systems.

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs\cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J, 
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled 
to a single notch-type\cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples\cite{majer2007coupling} the transmons and 
allows joint\cite{chow2010detecting} readout of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown 
depicting the layout of the components. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw''\cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in colour on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

\begin{figure}
	 	\includegraphics[width=\linewidth]{experiment_2}
	\caption{\textbf{(a)} Optical image of 
	the device (false coloured). Two transmons 
	(orange, 1 and blue, 2) are coupled 
	capacitively to a $\lambda/4$ coplanar 
	resonator. Frequency control lines come from 
	both sides, and from below a waveguide for 
	microwave excitation  is connected (green). 
	\textbf{(b)} The equivalent electrical 
	circuit. Tunable Josephson junctions are 
	SQUIDs with magnetic flux control. 
	\textbf{(c)} Frequencies of the fundamental 
	transitions of the transmons $\omega_1(I)$ 
	and $\omega_2(I)$ depending on the current 
	$I$ in an external coil when correctly 
	aligned by the individual flux control lines. 
	In this work, we focus on the area inside the 
	dashed rectangle.}
	\label{fig:experiment}
\end{figure}

@@

The readout resonator is not included in the 
model since in the dispersive regime it does not 
affect the dynamics of the SAM. Hence, the 
readout is modelled just by some measurement 
operator $\hat M(f_p)$ that can be obtained by 
finding the transmission $S_{21}(f_p)$ ($f_p$ is 
the probe frequency near the resonance) through 
the sample after preparing various states of the 
SAM. Another way to find $\hat M(f_p)$ is to 
calculate $S_{21}(f_p)$ via offsetting the 
experimental resonance curve measured when the 
SAM is in the ground state by the dispersive 
shifts corresponding to the SAM basis 
states\cite{filipp2009two, chow2010detecting}. Since we have not 
directly measured these dispersive shifts, in our 
modelling they are treated as fitting parameters. 
Finally, the observable value for any state $\hat 
\rho$ is calculated as $S_{21}^{sim}(f_p) = 
\Tr[\hat M(f_p) \hat \rho]$.

@@

	\includegraphics[width=.7\linewidth]{powerscan_1d}
	\caption{Power dependence of feature II: 
	experiment, simulation and analytic model. Dashed are the model curves turning to dotted when the 
	model is not expected to be valid (see 
	Sections \ref{sec:theory} and 
	\ref{sec:münchhausen}); model values for 
	$\Omega_{1,2}$ are the same for both (a) and 
	(b): $\Omega_{1,2}/2\pi=$ 4.5, 11.25, 22.5 
	and 45 MHz. \textbf{(a)} Experiment (second 
	cooldown; the parameters are different to 
	those in \autoref{fig:experiment}). The power 
	of the microwave source is increased from -20 
	to 0 dBm, and the corresponding growth of the 
	splitting and the widths of the spectral 
	lines is observed. \textbf{(b)} Simulation 
	with amplitudes of the driving $\Omega_{1,2}$ 
	equal to the model values; other parameters 
	as in \autoref{fig:two-tone}. Note that now 
	colours show the population of the ground 
	state. \textbf{(c)} Linear dependence of the 
	splitting size on the driving voltage of the 
	microwave source $V_{rms}$, ${\Omega_2}/{V_{rms}} = 0.23\ 
	{\text{MHz}}/{\text{mV}}$. From Section 
	\ref{sec:theory}, the splitting size is 
	$\frac{2\sqrt{3}}{3} \Omega_2$.}
	\label{fig:zoom}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{topological_splittings}
	\caption{Simulated population of the ground 
	state when the transmons are driven at the 
	same frequency but at different amplitudes 
	$\Omega_{1,2}$. In the top row (middle row), 
	$\Omega_{1(2)}$ is increased while 
	$\Omega_{2(1)} = \text{const},\ \Omega_{2(1)} \ll 
	\Omega_{1(2)}$; two topologically different 
	types of anticrossings arise depending on 
	which transmon is driven stronger. In the 
	bottom row, we show how the splittings vanish 
	when the weaker driving is increased to match 
	with the stronger one. Gray dashed lines show 
	the solution without driving, in black are 
	the model curves based on Sections 
	\ref{sec:theory} and \ref{sec:münchhausen}.}
	\label{fig:difdrive}
\end{figure*}

@@

\paragraph{Identification of the spectral lines.} 
Though it is not possible to describe all of the 
experimental features with the unperturbed model, 
we can still use it to identify most of the 
observed transitions as follows. By numerical diagonalization, we calculate the 
unperturbed frequencies of the undriven SAM as 
$\omega_{mn} = (E_n - E_m)/h$ where $n>m,\  
n,m=0..9$. In \autoref{fig:two-tone}~(d), we 
place them over the heatmap data optionally dividing 
$\omega_{mn}$ by some integer $n$ for $n$-photon processes. 
Since the number of SAM states is finite, we can 
quickly find all matches between the heatmap and the calculated eigenlevels.

@@

As one can see, various multiphoton transitions besides 
the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
$01$ and $10$ lines) are visible. The ${02/2}$ and ${20/2}$ 
are very commonly found for transmons and lie 
$|\alpha_{(1,2)}|/2$ lower than the main lines 
$\omega_{(1,2)}(I)$. Another two-photon process 
appears as $11/2$ line when two SAAs are excited 
simultaneously. This process is used, for 
example, for doing the bSWAP 
gate\cite{poletto2012entanglement}; in our case, 
it is taking part in feature I. A 
three-photon process $12/3$ is also clearly 
visible just below the $02/2$ line. As we will 
see, it is involved in forming features II and 
III. Notably, transitions $11/2$, ${21/3}$ and 
${12/3}$ are forbidden when there is no 
interaction between transmons ($J=0$). Therefore, 
it is expected that all Roman-numbered features 
should only appear with non-vanishing $\hat 
H_{int}$.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} 
	Schematic of the transition frequencies near 
	III (not to scale). Red dashed line shows the 
	current (0.36 mA) where the first transmon 
	(orange) is below the second one (blue) 
	exactly by $\alpha_2/2$ and several 
	transitions become resonant. Here we assume 
	that each transmon is driven at its own 
	frequency. \textbf{(b)} System level 
	structure at the resonant point and the first transmon 
	driving of amplitude $\Omega_1$ 
	(orange ellipses) at a small detuning 
	$\Delta_1$ from $\omega_1$. The second 
	transmon driving is not shown here. Action of 
	$\hat H_{int}$ in RWA is depicted as 
	orange-blue circles. \textbf{(c)} In the 
	frame rotating with $\hat 
	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
	become nearly degenerate ($\omega_1 
	\rightarrow \Delta_1$). Dressing increases this splitting to 
	$\Omega_1^R$. \textbf{(d)} Transitions in the 
	dressed system induced by $\hat 
	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
	the left part of the panel, all possible 
	two-photon transitions near $\omega_1$ are 
	depicted: the blue transitions are not 
	shifted in frequency, the light blue ones are shifted 
	by $\pm\Omega^R_1/2$. In the right 
	part, the most contributing trajectories are 
	depicted; gray crosses show transitions that 
	are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on which transitions
are involved in the A-T-like effect for feature III. 
For simplicity, we will temporarily assume that 
each transmon is driven at its own frequency 
(this assumption will be lifted in the following 
section). For convenience, in 
\autoref{fig:main_scheme}~(a) we schematically 
reproduce the transitions near III where the 
first transmon (orange) is below the second 
(blue), and the resonance point in current is 
shown with a dashed red line. Next, 
\autoref{fig:main_scheme}~(b) demonstrates the 
level structure of the SAM at 0.36 mA. Detuned by 
$\Delta_1$ from $\omega_1$, single-photon driving by 
$\hat H_d^1$ is shown with orange ellipses while 
much weaker two-photon driving by $\hat H_d^2$ is not shown because it does not alter the structure of energy levels. Since from numerical simulations we know 
that the third level of the first transmon is not 
necessary to observe the splitting, $\ket{20}$ is 
shown transparent, and states $\ket{21},\ 
\ket{22}$ are not shown.

@@

As one can see from \autoref{fig:difdrive}, near the 01, 10 intersection only the two-photon transition $11/2$ is affected and deviates from unperturbed spectrum while the spectral lines 01, 10 do not shift. Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b). We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously which is also clear from \autoref{fig:difdrive} where we observe one line to the left and the other to the right from the 01, 10 intersection.

@@

The upper branch of the fitted anticrossing is expected to deviate from the model (see \autoref{fig:zoom}) because of the avoided crossing marked as the secondary feature 3 which was not incorporated in the simple linear model. The small discrepancy between the experimental and simulated data in the upper branch is caused by a slight elevation of the lower sweet spot of the first transmon moving the avoided crossing 3 closer to the feature II; however, it is not important for our reasoning.

@@

Another interesting effect occurs when both 
components of the driving operator are in the 
single-photon regime. Now, both transmons are 
dressed and probed simultaneously. In this case, 
the $11/2$ transition is being split at the resonance between $01$ and $10$ into a hyperbolic curve, though never forming a doublet transition. The shape of the splitting and its visibility 
depends qualitatively on the relation between the driving 
amplitudes; for instant, if they are equal, the splitting does not appear at all. In our sample, we have a fixed ratio 
of approximately 2 between $\Omega_1$ and 
$\Omega_2$ which still allows us to distinguish the 
splitting experimentally. Notably, the frequency of $11/2$ transition far 
from resonance is also changed noticeably with 
changing power, which means that a fast bSWAP 
gate should be performed at a different frequency 
than the unperturbed model predicts.

@@

\begin{figure}[b]	
	\includegraphics[width=\linewidth]{intro_scheme}
	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame. \textbf{(a)} A three-level system is driven strongly by the coupler tone of amplitude $\Omega_c$ at frequency $\omega_c = \omega_{01}-\Delta$. \textbf{(b)} In the frame rotating with the drive changes, the $\ket{0}\rightarrow \ket{1}$ transition frequency changes to $\Delta$. However, when the RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\hbar \Omega^R$. Now, a doublet transition from these levels to the state $\ket{2}$ at frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$ may be observed.} 
	\label{fig:at-standard}
\end{figure}

\paragraph{Classical derivation.} In the classical case, the mathematical description goes as follows. At first, there is a three-level system which is driven by a strong radiation with an amplitude $\Omega_c$ at a frequency detuned by $\Delta$ from the $\ket{0}\rightarrow \ket{1}$ transition with a frequency $\omega_{01}$ (the \textit{coupler} tone). Additionally, we have a weak probe radiation at a frequency $\omega_{p}$ and with an amplitude $\Omega_p$ between $\ket{1}$ and $\ket{2}$ (the \textit{probe} tone). This step is illustrated in \autoref{fig:at-standard}~(a). The Hamiltonian for such system is as follows:

\begin{equation*}
\hat H_0/\hbar = \left[\begin{matrix}
0 & \Omega_{c} \cos{\left(\omega_{01}- \Delta \right)t} & 0\\
\Omega_{c} \cos{\left(\omega_{01} - \Delta \right)t}   & \omega_{01} &\Omega_{p} \cos\omega_p t  \\
0 & \Omega_{p} \cos{\omega_p t}  & \omega_{02}\end{matrix}\right].
\end{equation*}

Next, we move to the rotating frame by using an operator
\[
\hat R = \left[\begin{matrix} 
1 & 0 & 0\\0 & e^{- i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{- i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
\]
Note here that level $\ket{2}$ is also rotated: this is convenient to preserve the frequency of the driving term with $\Omega_p$. The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat R^\dag \hat H_0 \hat R - i \hat{R}^\dag \partial_t  \hat R$. The level structure without driving  is shown in the left part of \autoref{fig:at-standard}~(b). Applying the RWA, we obtain:
\begin{equation*}
\hat H_1/\hbar = \left[\begin{matrix}0 &\Omega_{c}/2 & 0\\\Omega_{c}/2 & \Delta & \Omega_{p} e^{i t \omega_p}/2\\0 & \Omega_{p} e^{-i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
\end{equation*}

@@

\begin{equation*}
\hat H_3/\hbar = \left[\begin{matrix} 
\frac{\Delta}{2} - \frac{\sqrt{\Delta^{2} + \Omega_{c}^{2}}}{2} & 
0 &
\frac{\Omega_{p} e^{i t \omega_{p}}}{2}\sin(\theta)
\\
0 & 
\frac{\Delta}{2} + \frac{\sqrt{\Delta^{2} + \Omega_{c}^{2}}}{2} & 
\frac{\Omega_{p} e^ {i t \omega_p}}{2}\cos(\theta)
\\
\frac{\Omega_{p} e^{-i t \omega_{p}} }{2}\sin(\theta) & 
\frac{\Omega_{p} e^{-i t \omega_{p}}}{2} \cos(\theta) & 
\omega_{12} +\Delta 
\end{matrix}\right].
\end{equation*}

One may see that now resonant conditions for the probe drive are $\omega_p = \omega_{12} + {(\Delta \pm \Omega^R)}/{2}$, where $\Omega^R = \sqrt{\Omega_c^2 + \Delta^2}$, $\omega_{12} = \omega_{02}- \omega_{01}$, and its amplitude is renormalized by an angle $\theta,\ \tan 2\theta = -\Omega_c/\Delta$.
